On the formation of H$\alpha$ line emission around classical T Tauri stars

### 2006-01-27 TTau_Halpha/kurosawa.tex
Change in appendix.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@641 25464f21-6099-402c-b30a-640f1d40d38b

    \includegraphics[%
      clip,
      scale=0.45,angle=270]{figures/discwind_hybrid_ha_image2.eps}

@@

    \begin{tabular}{cc}
      \includegraphics[%
	clip,
	scale=0.45]{figures/discwind_acc_inc_effect_m9_b1_t7000.eps}&
      \includegraphics[%
	clip,
	scale=0.45]{figures/stellarwind_inc_effect.eps}\tabularnewline
    \end{tabular}

@@

Here we present xxxxxxxxxxxxxxx.

>>>>

    \includegraphics[%
      clip,
      scale=0.45,angle=270]{figures/discwind_hybrid_ha_image.eps}

@@

    \begin{tabular}{cc}
      \includegraphics[%
	clip,
	scale=0.45]{figures/discwind_acc_inc_effect_m9_b1_t7000.eps}&
      \includegraphics[%
	clip,
	scale=0.61]{figures/stellarwind_inc_effect.eps}\tabularnewline
    \end{tabular}

@@

Additional H$\alpha$ model line profiles 
computed using disc-wind-magnetosphere hybrid model
(section~\ref{sub:result-discwind-hybrid}) are presented here.  All
the models use the reference parameters for the 
magnetospherical geometry and the photosphere as given in
Table~\ref{tab:std_paramters} in the main text. The ratio ($\mu$) of the
mass-loss rate to mass-accretion rate is fixed to 0.1 for the all 
models. Three sets of model profiles, each with a different
mass-accretion rate, are presented here: 
(1) $\dot{M}_{\mathrm{acc}}=10^{-7}\,M_{\sun}\,\mathrm{yr^{-1}}$ (Figure~\ref{fig:atlas01}), 
(2) $\dot{M}_{\mathrm{acc}}=10^{-8}\,M_{\sun}\,\mathrm{yr^{-1}}$ (Figure~\ref{fig:atlas01}), and
(3) $\dot{M}_{\mathrm{acc}}=10^{-7}\,M_{\sun}\,\mathrm{yr^{-1}}$
(Figure~\ref{fig:atlas01}).   The temperature of the magnetosphere
used for (1), (2) and (3) are $7500\Kelvin$, $8500\Kelvin$ and
$9500\Kelvin$ respectively.  The corresponding wind mass-loss rates
are used for $\mu=0.1$. In each set the profiles are presented for the
inclination angle of $10^\circ$, $55^\circ$, and $80^\circ$. 
The disc-wind geometry used to compute these profiles are same as in
section~\ref{sub:result-discwind-hybrid}.
